### 2014-02-27 paper/retrofit.tex
thm as def

\begin{figure}
  Concurrent, round robin:
\begin{code}
  sched step (it1, it2, ldots)  = it2, ldots, it1
  sched D (it1, it2, ldots)     = it2, ldots
  sched N (it1, it2, ldots)     = it2, ldots
  sched F (it1, it2, ldots)     = it2, ldots, it1
\end{code}
  Sequential:
\begin{code}
  sched step (it1, it2, ldots)     = it1, it2, ldots
  sched N (it1, it2, ldots)        = it1, it2, ldots
  sched D (it)                     = it
  sched D (it1, it2, ldots)        = it2, ldots
  sched F (it1, it2, ldots, itn)   = itn, it1, it2, ldots
\end{code}
\caption{Scheduling policies}
\end{figure}

@@

\begin{theorem}[Termination Sensitive Non-Interference (TSNI)]
  For any configurations |ic1|, |ic1'|, |ic2|, and label |il| where
  \begin{equation} \label{eq:tsni-lhs}
    |ic1| \approx_{|il|} |ic2|
    \qquad \text{and} \qquad
    |ic1| |.->|^* |ic1'|
  \end{equation}
  then there exists a configuration |ic2'| such that
  \begin{equation} \label{eq:tsni-rhs}
    |ic1'| \approx_{|il|} |ic2'|
     \qquad \text{and} \qquad
    |ic2| |.->|^* |ic2'|
    \ \text{.}
  \end{equation}
\end{theorem}

@@

>>>>

\begin{figure}
  Concurrent, round robin:
\begin{code}
  roundrobin step (it1, it2, ldots)  = it2, ldots, it1
  roundrobin D (it1, it2, ldots)     = it2, ldots
  roundrobin N (it1, it2, ldots)     = it2, ldots
  roundrobin F (it1, it2, ldots)     = it2, ldots, it1
\end{code}
  Sequential:
\begin{code}
  seq step (it1, it2, ldots)     = it1, it2, ldots
  seq N (it1, it2, ldots)        = it1, it2, ldots
  seq D (it)                     = it
  seq D (it1, it2, ldots)        = it2, ldots
  seq F (it1, it2, ldots, itn)   = itn, it1, it2, ldots
\end{code}
\caption{Scheduling policies}
\end{figure}

@@

\begin{definition}[Information-flow control language]
    An information-flow control language |L| is a tuple $(|C|, |C|^*, |.->|,
    |erasef l|)$, where $c \in |C|$ is the type of machine configurations,
    $|C|^*$ is the type of erased machine configurations, |.->| is a
    reduction relation between machine configurations and $|erasef l|$
    is an erasure function from machine configurations to erased machine
    configurations.  For sequential languages, we may also speak of
    values, e.g. a configurations $V \subseteq |C|$ for which there are
    no possible further transitions.
\end{definition}

\begin{definition}[$l$-equivalence]
    Two machine configurations $c$ and $c'$ are considered $l$-equivalent ($c \approx_l c'$)
    if $|erase l c| = |erase l c'|$.
\end{definition}

\begin{definition}[Termination Sensitive Non-Interference (TSNI)]
  A language $|L|=(|C|, |C|^*, |.->|, |erasef l|)$ is termination
  sensitive non-interfering if for any label |l|, and configurations
  |c1, c1', c2 member C|, if
  \begin{equation} \label{eq:tsni-lhs}
    |c1| \approx_{|l|} |c2|
    \qquad \text{and} \qquad
    |c1| |.->|^* |c1'|
  \end{equation}
  then there exists a configuration |c2' member C| such that
  \begin{equation} \label{eq:tsni-rhs}
    |c1'| \approx_{|l|} |c2'|
     \qquad \text{and} \qquad
    |c2| |.->|^* |c2'|
    \ \text{.}
  \end{equation}
\end{definition}

\begin{theorem}[TSNI]
\end{theorem}

@@

\begin{definition}[Termination Insensitive Non-Interference (TINI)]
  A language $|L|=(|C|, |C|^*, |.->|, |erasef l|)$ is termination
  insensitive non-interfering if for any label |l|, and configurations
  |c1, c2, V1, V2 member C|, if
   $|c1| \approx_{|l|} |c2|$,
   $|c1| |.->|^* |V1|$, and
   $|c2| |.->|^* |V2|$, then
   $|V1| \approx_{|l|} |V2|$.
\end{definition}
